The Implications of Local Fluctuations in the Galactic Midplane for Dynamical Analysis in the \textit{Gaia} Era

### 2019-07-26 paper/ms.tex
Update ackowledgements
Clean up/fix discussion of energy error

\textbf{Because the energies in the radial and vertical coordinates are related to the
radial and vertical actions by a constant
%mm (Equation~\eqref{eq:JR_Jz_epi_energy}),
    (Eq.~[\ref{eq:JR_Jz_epi_energy}])
the fractional error
%mm on
     in
these two
energies
%mm in the as in the actions. The
%[I am guessing as to what this means, so **** check ****]
      evolves in the same way as the actions.  We can see this because the
 energy in the azimuthal coordinate can
be readily computed,
%mm [maybe give it here to ensure that everyone is on the same page?]
%mm and we therefore conclude that
    so
for the given offsets the error
%mm on
    in
the total computed energy is
\beq\label{eq:error_total_energy}
\frac{\Delta E}{E} = \frac{\Delta J_R}{J_R} + \frac{\Delta J_{\phi}}{J_{\phi}}
                     + \frac{\Delta J_z}{J_z}\text{.}
\eeq}

@@

\acknowledgments
We thank the anonymous referee for providing helpful comments. We would like
to thank Megan Bedell, Robert A. Benjamin, Maria Bergemann, Joss
Bland-Hawthorn, Tobias Buck, Elena D'Onghia, Benoit Famaey, and Adrian
Price-Whelan for helpful discussions. A.B. would like to thank Todd Phillips
for helpful discussions. This work uses data hosted by the Flatiron
Institute's FIRE data hub. This project was developed in part at the 2019
Santa Barbara Gaia Sprint, hosted by the Kavli Institute for Theoretical
Physics (KITP) at the University of California, Santa Barbara. This research
was supported in part at KITP by the Heising-Simons Foundation and the
National Science Foundation (NSF) under Grant No. PHY-1748958. This work used
the Extreme Science and Engineering Discovery Environment (XSEDE), which is
supported by NSF Grant No. OCI-1053575. A.B. was supported in part by the Roy
\& Diana Vagelos Program in the Molecular Life Sciences and the Roy \& Diana
Vagelos Challenge Award. K.V.J.'s contributions were supported in part by the
NSF under Grant No. AST-1614743. M.-M.M.L. was partly supported by the NSF
under Grant No. AST-1815461.

>>>>

\textbf{Because the energies in the radial and vertical coordinates are
related to the radial and vertical actions by a constant
(Equation~\eqref{eq:JR_Jz_epi}), the fractional error in these two energies is
the same as the actions. The energy in the azimuthal coordinate can be readily
computed ($E_{\phi} = \frac{1}{2}v_{\phi}^2$), and we therefore conclude that
the error induced in the total energy is:
\beq\label{eq:error_total_energy}
\frac{\Delta E}{E} = \frac{\Delta J_R}{J_R} + 2\frac{\Delta J_{\phi}}{J_{\phi}}
                     + \frac{\Delta J_z}{J_z}\text{.}
\eeq}

@@

\acknowledgments
We thank the anonymous referee for providing helpful comments. We would like
to thank Megan Bedell, Robert A. Benjamin, Maria Bergemann, Joss
Bland-Hawthorn, Tobias Buck, Elena D'Onghia, Benoit Famaey, and Adrian
Price-Whelan for helpful discussions. A.B. would like to thank Todd Phillips
for helpful discussions. This work uses data hosted by the Flatiron
Institute's FIRE data hub. The Flatiron Institute is supported by the Simons Foundation. This project was developed in part at the 2019
Santa Barbara Gaia Sprint, hosted by the Kavli Institute for Theoretical
Physics (KITP) at the University of California, Santa Barbara. This research
was supported in part at KITP by the Heising-Simons Foundation and the
National Science Foundation (NSF) under Grant No. PHY-1748958. This work used
the Extreme Science and Engineering Discovery Environment (XSEDE), which is
supported by NSF Grant No. OCI-1053575. A.B. was supported in part by the Roy
\& Diana Vagelos Program in the Molecular Life Sciences and the Roy \& Diana
Vagelos Challenge Award. K.V.J.'s contributions were supported in part by the
NSF under Grant No. AST-1614743. M.-M.M.L. was partly supported by the NSF
under Grant No. AST-1815461.
